Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2016-11-23 paper.tex
Add figure for homogeneous isotropic test

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-homogeneous_isotropic}
  \caption{
    Equilibrium distribution functions in a homogeneous background at
    $\varrho=6.22 \times 10^{12}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=5$~MeV,
    $Y_e=0.3$,
    using the LS220 equation of state, in which the equilibrium
    neutrino chemical potentials are
    $\mu_{\nu_e}=-\mu_{\bar{\nu}_e}=62.04$~MeV, and 
    $\mu_{\nu_x}=0$.
    The solid lines give the analytic Fermi-Dirac distribution,
    and the points are computed via ray tracing.}
  \label{fig:homogeneous_isotropic}
\end{figure}
